A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-04-25 Cover_letter_JPM.tex
start extended revision

\documentclass[preprint,12pt]{elsarticle}
% major revision and answer question (3 reviewers)
%Sunday, January 24⋅22:30 – 22:55
%Daily, until Jan 29, 2021

@@

\section*{Cover letter for the revision (cancers-1082127)} % 2021/01/25
%其實直接 online 填寫即可
%Please provide a cover letter to explain point-by-point the details of the revisions [changes 摘要即可 from the rebuttal]  in the manuscript

%Assistant Editor
%E-Mail: aubree.zhu@mdpi.com
%MDPI Branch Office, Tianjin
Assistant Editor of Cancers%\newline

Feb 2, 2021

Dear Dr. Aubree Zhu:

Enclosed, please find our revised manuscript (cancers-1082127) entitled "A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma" by Chi et al., which we wish to be considered for publishing as a research article in Cancers. We appreciate your time serving as the editor handling this manuscript and thank the reviewers for their critical comments and suggestions on our manuscript.

We have since performed the additional literature review and revised the manuscript accordingly to address their critical comments and suggestions in a point-by-point manner,

@@

According to the editor's comments, we have the manuscript checked for English grammar and reformatted Table 1 by rotating 90 degrees to portrait mode. %
We wish our revised manuscript could be satisfied and accepted for publication in Cancers. Thanks very much for the kind helps and the reviewers' critical comments.
%\\[0.4cm]
Kind regards,

@@

\section*{Response to Reviewer 1 Comments}
%Response to Referees} % rebuttal
We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript. The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}). 
Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.
%Reviewer #1(Technical Comments to the Author):
%   The ms investigates an interesting and timely topic. However, the discovery cohort involves a small sample size and throughout the analysis, the issue of correcting the obtained p-values for multiple comparisons is not addressed. Hence, the evidence for zooming into TMSB4X is not convincing.

%\section{Responses to Reviewers' comments}
% our responses to the reviewers' comments.
%***Response to reviewer's comments: [藍色字]

Comments from the reviewer \#1:

The authors have described the effectiveness of RNA sequencing as a tool for exploring prognostic factors; they have also performed a large-scale analysis using the TCGA cohort, which is a very attractive analysis method. I have a few minor questions.

This is an attractive analysis method and I would like to know more details.

\subsection*{1-1}
It is generally known that high expression of EGFR is a poor prognostic factor in head and neck cancers, however, why is it that RNA sequencing does not identify RNA coding for EGFR as a poor prognostic factor?

@@

We appreciate the reviewer for the critical comments and thanks for the agreement with our analysis using the TCGA cohort.
%[我的 candidate 中為什麼沒有 EGFR];  
In our analysis, the \acrshort{egfr} is ranked at 5707 from 20500 protein-coding genes %5708-1
by Kaplan-Meier estimate with the log-rank test P-value as 0.0495. The \acrshort{egfr} is identified as one of those poor prognostic factors as well. %However, it is far from the top 20 candidates.
(please see https://github.com/texchi2/\linebreak
pvalueTex/blob/master/HNSCC\_OS\_marginS\_6429.csv for reference, the table was ranked by FDR P-value)

% transforming growth factor- (TGF-α) 
% epidermal growth factor receptor (EGFR)
As in our manuscript mentioned, 
In a multivariate analysis, tumor site, tumor level of \acrshort{egfr}, and tumor level of TGF-$\alpha$ (\acrshort{egfr} ligand) were statistically significant predictors of disease-free survival of \acrshort{hnscc} patients\cite{Rusch1996}\cite{Grandis1998}.
Since that breakthrough discovery and validation, the \acrshort{egfr} monoclonal antibody (cetuximab)\cite{Bonner2006a} and \acrshort{egfr} \acrshort{tki} (such as gefitinib, erlotinib, osimertinib) were developed to treat advanced \acrshort{hnscc}. Although 90\% of \acrshort{hnscc} has overexpression of \acrshort{egfr}, cetuximab has only 10\% to 20\% response rate on those patients\cite{Johnson2020}. So far, cetuximab is still the only drug of choice with proven efficacy, which targeted the selected \acrshort{hnscc} patients\cite{Taberna2019}.
%citing the line number and exact change, marked in \textcolor{red}{Red from page 6 (line 16) to page 7 (line 17)}
Thus, we wish the further validations of our meaningful hypotheses of the candidate to explore more useful drug of choice in the treatment of \acrshort{hnscc} patients.
% a list from literature review, 留 下少於  50 articles mentioned candidates
%HNSCC_survivalAnalysis_marginS_EGFR.Rda
%HNSCC_survivalAnalysis_marginS_EGFR.xlsx
%https://github.com/texchi2/pvalueTex/blob/master/file20500_list.txt
%analysis_export.R to generate https://github.com/texchi2/pvalueTex/blob/master/HNSCC_OS_marginS_6429.csv
\end{MyColorPar}

\subsection*{1-2}
DNA alteration (mutation/amplification) is also an influential prognostic factor, but I would like to know if DNA alteration is considered in this analysis.
%[如果加入 DNA alteration 又會如何? 不佳; 選擇 mRNA 的原因是? interpretability and drugable: EGFR]

@@

We appreciate the reviewer for reminding the importance of DNA alteration in survival analysis.
Those different types of omics data measured for the same patients (called multi-omics data) are currently under investigation across several disciplines such as genomics (i.e., DNA mutation/amplification, single nucleotide polymorphisms), %copy number variation), 
epigenomics, transcriptomics (i.e., RNA expression), proteomics, metabolomics, and microbiomics.
The usefulness of multi-omics data for the prediction of HNSCC outcome is expected.
%such as the (censored) survival time.
Moritz Herrmann et al.(2020) observed that using multi-omics and survival data can slightly improve prediction methods for particular datasets, such as TCGA HNSCC\cite{Herrmann2020}.
%It is limited that the utility of multi-omics data for prediction purposes in the considered TCGA studies\cite{Herrmann2020}.
%18 cancer datasets from The Cancer Genome Atlas (TCGA) 
According to their study, %the multi-omics structure have a slightly better prediction performance than naive (0.562 vs. 0.557 ) with favoring clinical variables leads to better prediction results for HNSCC. %likelihood-based boosting (CoxBoost and CoxBoost favoring)
% Exemplary t-tests comparing blockForest with CoxBoost favoring and the Clinical only model showed no significant differences in performance. 
% blockForest also offers the possibility of favoring clinical covariates using the argument always.select.block of the blockfor function
%Last but not the least, multi-omics data are structured: the variables are partitioned into (non overlapping) groups. 
% ***
the survival analysis of the TCGA HNSCC dataset by blockForest method (with multi-omics and clinical variables) has a similar prediction performance than Cox's model (with clinical variables alone). %from The Cancer Genome Atlas (TCGA) 
They also reported the performance C-index as 0.582 [CI: 0.554, 0.610] in blockForest method and 0.554 [CI: 0.519, 0.588] in Cox's model\cite{Herrmann2020}.

% 小心光茫太甚  Well-established prognostic clinical variables: prioritize
% the number of variables in the group of variables of TCGA HNSCC dataset:
% 11 clinical variables, 57964 CNV variables, 17248 mutation variables and 21520 RNA expression variables.
%*** Taking this structure into account can protect the predictive information that transcriptomics (e.x. RNA-Seq) or low-dimensional clinical variables might get lost within the huge amount of genomics (e.x. DNA mutation/amplification, copy number variation) data\cite{Boulesteix2011}\cite{Herrmann2020}.
DNA amplification will usually be one of the causes to overexpress the gene.
Moreover, transcriptomics study is helpful in drug discovery. For example, the overexpressed gene is possible to be a drug-targetable candidate\cite{Park2015}. After thoughtful validation in vitro/in vivo then pathway study, the EGFR inhibitory leads were constructed by antibody design or chemical compound screening\cite{Mahajan2016}. %比較容易研發 clinical and transcriptomics by ssurvival::survfit and urvival::coxph
% the selection of clinical features by domain knowledge and studies where HNSCC was under investigation.
The discovery of EGFR inhibitors\cite{Bonner2006a} for HNSCC therapy will encourage the research community to conduct the survival analysis under abnormality in gene expression.

% *** it needs deep learning, but less interpretability (yet under development\cite{Chaudhary2018}) (DNA+RNA and clinical dataset => multi-omics cancer study)
%high dimensional multi-omics analysis by deep learning 
%It may be beneficial to include these different data types in models predicting outcomes, such as the survival time of patients. Until recently, only data from a single omics type were used to build such prediction models, with or without the inclusion of standard clinical data [2]. In recent years, however, the increasing availability of different types of omics data measured for the same patients (called multi-omics data from now on) has led to their combined use for building outcome prediction models. An important characteristic of multi-omics data is the high-dimensionality of the datasets, which frequently have more than 10 000 or even 100 000 variables. This places particular demands on the methods used to build prediction models: they must be able to handle data where the number of variables by far exceeds the number of observations. Moreover, practitioners often prefer sparse and interpretable models containing only a few variables [3]. Last but not the least, multi-omics data are structured: the variables are partitioned into (nonoverlapping) groups. This structure may be taken into account when building prediction models.
%Citation: https://academic.oup.com/bib/advance-article/doi/10.1093/bib/bbaa167/5895463
%特別的 algorithm 
%however, interpretation and practical application of the model to the prediction of independent data are easier with regression-based methods yielding coefficients that reflect the effects of variables on the outcome than with machine learning algorithms [8].
%Multi-omics data, that is, datasets containing different types of high-dimensional molecular variables; they must be able to handle data where the number of variables by far exceeds the number of observations.
%https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6419526/
%Deep learning
%SALMON (Survival Analysis Learning with Multi-Omics Neural Networks)

%\cite{Lawrence2015a} TCGA HNSCC %的第一篇文章已經分析過 DNA mutation of HNSCC
%Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature, 517(7536), 576–582. 
%https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/publications
%=> HNSCC marker paper\cite{Lawrence2015a}

%The presence of widespread genomic instability in HNSCC, such as cytogenetic aberrations, allelic imbalance/loss of heterozygosity, and microsatellite instability (MSI), suggests that there is an imperfection in the host DNA repair machinery. Genomic instability with progressive accumulation of detrimental genetic alterations appears to be dependent upon a circuitous interaction between the environmental genotoxic insults and the host DNA repair machinery, the functional integrity of which is governed by the proper cell cycle control and host DNA repair capacity. Genomics allows the identification of possibly relevant variants, such as single nucleotide polymorphisms (SNPs), copy number variation (CNV), mutations and translocations => %https://cancersheadneck.biomedcentral.com/articles/10.1186/s41199-020-0047-y
%DNA mutation: copy number burden (CNB) and tumor mutation burden (TMB) are important for predicting tumor progression (Marshall et al., 2017; Thomas et al., 2018)
% *** The Landscape of Somatic Copy Number Alterations in Head and Neck Squamous Cell Carcinoma, 2020. => 18 GEO dataset (873 patients from GEO) + TCGA: chromothripsis 6\%\cite{Yang2020}
%metaanalysis of NCBI GEO database (https://www.ncbi.nlm.nih.gov/geo/). We integrated the following datasets: TCGA-HNSCC, GSE11938, GSE20306, GSE20939, GSE23831, GSE25103, GSE31984, GSE33229, GSE33983, GSE34507, GSE36790, GSE39367, GSE40777,GSE47443, GSE51265, GSE57201, GSE66136, GSE68717, and GSE85514.

%TMB: To calculate TMB, you need to know the total size of the region sequenced. If data is from exome sequencing, you would find the size of the exome capture, and divide total mutations (or non-synonymous only depending on strategy), by that size (e.g. ~45MB) to get SNV/MB ratio.
%tumor mutational burden-high (TMB-H) [≥10 mutations/megabase (mut/Mb)] in solid tumors (criteria for pembrolizumab)
%Identification of Genomic Predictors for Treatment Response to Cancer Immunotherapy Using Omics Data Analysis (Yu-Chao Wang)
%=> ICIs criteria <- TMB <- DDR DNA repair gene
\end{MyColorPar}
\pagebreak
%======
\section*{Response to Reviewer 2 Comments}
%Response to Referees} % rebuttal
We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript. The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}). 
Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.

Comments from the reviewer \#2

How representative is the TCGA database for HNSCC?

Can be the found positive and negative prognostic genes underlined by comparable studies using other databases than TCGA?

Could the authors summarize the elements of the workflow that could be used on any database independently from TCGA?

Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.

%[找出其他 database cohort 的比較]
\subsection*{2-1}
How representative is the TCGA database for HNSCC?

@@

We appreciate the reviewer for the question allowing discussing TCGA in detail.\\
To the best of our knowledge, TCGA "HNSC"(they coded) is the only single and largest collection of whole-genome sequencing and clinical survival dataset in the field of HNSCC research so far.
When we queried from the Embase database using the MESH words "HNSCC AND TCGA," simple statistics show a total of 12,636 research articles/conference abstracts for HNSCC from 2008 to 2021, since the first TCGA article was published on 2008\cite{McLendon2008} by TCGA research network.
After that, there are 18,082 cross-cancer type articles produced using the TCGA database. The 778 publications (Figure \ref{figure:fig_embase}, b. 778) among them were focused on HNSCC research. Those occupied about 18\% of HNSCC research articles with genetic-related topics during the same time. Thus, about 60 TCGA HNSCC articles were published worldwide per year since 2008. %\ref{figure:fig_embase}
\begin{figure}
\raggedleft
\includegraphics[width=14cm]{Answer_2-1.pdf}
\caption{Cancer research articles published from 2008 to 2021. Total: 2.4 million; genetic related: 0.6 million; HNSCC research: 12,636.}
\label{figure:fig_embase}
\end{figure}
\clearpage
%778/4350 = 17.9\% using TCGA data
%There is 374 genes in the oral cancer gene database of Indian HNSCC; http://www.bioinformation.net/006/97320630006169.pdf
%http://www.actrec.gov.in/OCDB/index.htm

@@

\subsection*{2-2}
Can be the found positive and negative prognostic genes underlined by comparable studies using other databases than TCGA?

@@

We appreciate the reviewer for the critical comment.
We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
The GSE2837 carries
% VUMC, VAMC, UTMDACC (1992-2005)
relapse-free survival (RFS) data, instead of overall survival in TCGA dataset,
and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
The survival significance (Kaplan Meier P-value) is in the following probes of 10 genes:\\
1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
%17 out of 20 candidates
%?DKK1 (0.253635), 
Please see Figure \ref{figure:fig_GSE2837}.
Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
The 10 out of 20 positive and negative prognostic genes underlined are confirmed by comparable studies using GSE2837 dataset other than the TCGA cohort.

@@

\subsection*{2-3}
Could the authors summarize the elements of the workflow that could be used on any database independently from TCGA?

@@

%how to apply or modify the R scripts to use on other datasets
%\begin{itemize} %summarize the elements of the workflow
\begin{outline}
The data from TCGA database or other databases could be applied by this workflow, since modification of the R script is necessary to adapt the difference structure among datasets (e.x. data schema, table size, definition of features, number of features and their location on the table column).\\
In short, the elements of the workflow with the \{codes\} shows:\\
(please also see Figure \ref{fig:workflow})
\1 $[\# step 1 (main)]$
\{main\_marginSFP\_HNSCC.R\}
        \2 dataset retrieval from TCGA GDC data portal (in GDAC format)
%\1 $[\# step 1]$
    \2 \{TCGA\_HNSCC\_marginSFP.R\}
        \3 \underline{raw data cleaning}
        \3 \underline{data transformation and merge}
        \3 \underline{dichotomization of clinical features}
%     \item Using a serial cut from 30\% to 70\% percentile of the cohort, it could find the least P-value cutoff of the Kaplan-Meier analysis for each gene expression.
        \3 survival analysis
            \4 cut off finder by \{cutofFinder\_func\_HNSCC.R\}
%     \item The R script program could automatically scan protein-coding genes and generate the Kaplan-Meier plots and Cox's univariate/multivariate tables.
            \4 Cox modelling
\1 $[\# step 2]$
\{analysis\_export.R\}
    \2 analysis of the tables generated from \# step 1
    \2 candidate selection
%    \item Our analysis could discover the pronounced biomarkers, which impact HNSCC's survival under the stringent Bonferroni adjustment.
\1 (remark: only the \underline{underlined} portion in \{TCGA\_HNSCC\_marginSFP.R\} should be re-coded aggressively)
\end{outline}

@@

% #####################
\subsection*{2-4}
Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.

@@

"The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005.
TCGA represents comprehensive genomics and clinic data from 84,392 patients among 33 major cancer types (data release 27.0 - Oct 29, 2020, available at https://www.cancer.gov/about-nci/\\organization/ccg/research/structural-genomics/tcga/studied-cancers).
%The Cancer Genome Atlas (TCGA): The TCGA consortium, which is a National Institute of Health (NIH) initiative, makes publicly available molecular and clinical information for more than 33 types of human cancers including exome (variant analysis), single nucleotide polymorphism (SNP), DNA methylation, transcriptome (mRNA), microRNA (miRNA) and proteome.

TCGA and other collaborated \acrfull{gdac} generated and analyzed DNA (mutation, copy number variation, methylation, simple nucleotide polymorphism, SNP), RNA (microarray, RNA-Seq, microRNA), and protein (reverse protein phased array) data derived from biospecimen. Sample types available at TCGA are primary solid tumors, recurrent solid tumors, blood-derived normal and tumor, metastatic, and solid tissue normal.

The NCI's Genomic Data Commons (GDC, available at https://portal.\\gdc.cancer.gov/) receives, processes, and distributes genomic, clinical, and biospecimen data from TCGA database and other cancer research programs. The clinical features has been defined by \acrshort{tcga} \acrshort{gdc} data dictionary: \acrfull{cde}\cite{CDE2019}. The \acrshort{rnaseq} expression data has been harmonized and re-aligned against an official reference genome build (\acrlong{grch38}, \acrshort{grch38}).
%The old TCGA data portal (https://tcga-data.nci.nih.gov/docs/publications/tcga/) stops updating and all TCGA data was transferred to the GDC data portal .
\acrshort{tcga}, GDC and research community offer several computational tools to the public for facilitating cancer research. %There is three categories of tools to approach the TCGA data from GDC.

GDC Data Portal (available at https://portal.gdc.cancer.gov) is the official web-based TCGA data analysis tools. Other available web-based tools have been reviewed by Zhang et al.\cite{Zhang2019b} and 
Matthieu Foll (availalbe at https://github.com/IARCbioinfo/awesome-TCGA).
One of \acrshort{gdac}s, the Broad TCGA Data and Analyses (Broad GDAC), provides Firehose, a repository of the TCGA public-accessible Level 3 data and Level 4 analyses. Broad GDAC Firehose is an analytical infrastructure that analyses algorithms not performed by the GDC (e.x. GISTIC, MutSig2CV, correlation with clinical variables, mRNA clustering). 
A web-based version of Broad GDAC Firehose is Firebrowse (available at firebrowse.org, Version: 1.1.40, 2019-10-13).

%Python and UNIX bindings
%R bindings
Broad GDAC Firebrowse provides graphical tools like viewGene to explore expression levels and iCoMut to explore a mutation analysis of each TCGA disease.

%Second, GDC data transfer tool (available at https://gdc.cancer.gov/access-data/gdc-data-transfer-tool) allows users to access the open or controlled data. %the GDC data model, data formats
% RESTful API

GDC \acrfull{api} is designed under the \acrfull{rest} architecture and provides accessibility to external users for programmatic access to the same functionality found through GDC Portals. Those functions include searching, viewing, submitting, and downloading subsets of data files, metadata, and annotations based on specific parameters. Moreover, if restricted data is requested, the user must provide a token along with the API call. This token can be downloaded directly from the GDC Portals. (courtesy of the National Cancer Institute)
Broad GDAC Firebrowse \acrshort{rest}ful \acrshort{api} could be accessed using an R package, FirebrowseR (available at https://github.com/mariodeng/FirebrowseR)\cite{Deng2017}.

>>>>

\documentclass[preprint,12pt]{elsarticle}
% Extended revision and answer question (2 reviewers)
% for JPM-1174473
%Since April 19, 2021
%Please resubmit your revised manuscript through the following link:
% https://susy.mdpi.com/user/manuscripts/upload?pre_hash_key=6f6b5248032093559a0cdfda5026f51f

@@

\section*{Cover letter for the re-submission (jpm-1174473)} 
% 2021/04/25
% 直接 online 填寫即可
%Please provide a cover letter to explain point-by-point the details of the revisions [changes 摘要即可 from the rebuttal]  in the manuscript

%Assistant Editor
%Suite 305, Zhongjia Mansion, Building No.13, Taiyangyuan Community, Dazhongsi 
%East Road,
%Haidian District, Beijing 100190, China
%Email: sonia.sun@mdpi.com
Assistant Editor of JPM%\newline

April 30, 2021

Dear Ms. Sonia Sun:

Enclosed, please find our revised manuscript (jpm-1174473) entitled "Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma" by Chi et al., which we wish to be considered for publishing as a research article in Journal of Personalized Medicine. We appreciate your time serving as the editor handling this manuscript and thank the reviewers for their critical comments and suggestions on our manuscript.

We have since revised the manuscript accordingly to address their critical comments and suggestions in a point-by-point manner,

@@

According to the editor's comments, we have the manuscript checked for English grammar. %
We wish our revised manuscript could be satisfied and accepted for publication in JPM. Thanks very much for the kind helps and the reviewers' critical comments.
%\\[0.4cm]
Kind regards,

@@

\section*{Response to Reviewer 1 Comments}
%Response to Referees} % rebuttal
We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript. The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}). 
Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.

Comments and Suggestions for Authors from the reviewer \#1:

This manuscript perhaps describes the biomarkers of head and neck SCC using several data-bases. They also describe the relationship between the expression level of each candidate biomarkers in their patients and other factors such as gender, age, margin, lymph-node metastasis and so on.
%=> RNA expression and other contributing factors in the survival of HNSCC patients

I myself think this manuscript is very interesting, however, I do not find the difference between the previously published manuscript from your institute.
https://www.researchsquare.com/article/rs-80673/v1

\subsection*{1-1}
First of all, please describe the difference between the two manuscripts.

%The authors have described the effectiveness of RNA sequencing as a tool for exploring prognostic factors; they have also performed a large-scale analysis using the TCGA cohort, which is a very attractive analysis method. I have a few minor questions.

%This is an attractive analysis method and I would like to know more details.

%It is generally known that high expression of EGFR is a poor prognostic factor in head and neck cancers, however, why is it that RNA sequencing does not identify RNA coding for EGFR as a poor prognostic factor?

@@

We appreciate the reviewer for the critical comments and thanks for the agreement with our analysis using the TCGA cohort.

The manuscript posted in the preprint server, ResearchSqaure, is our first version (2020/09/28) of current manuscript. 
Since previous reviewer's suggestion, we made a major revision on the followings:
1) suggested  candidates of biomarker has been modified  by additional validation using an independent patient cohort (GSE2837).
We also reviewed literature that supports the prognostic impact of these candidate genes. The resulting Figure 4, Table 3 and Table 4 is different between the two manuscripts.
2) Since that revision, we extended holistic cancer care in the discussion section (please see Answer 1-2).

%[我的 candidate 中為什麼沒有 EGFR];  
%In our analysis, the \acrshort{egfr} is ranked at 5707 from 20500 protein-coding genes %5708-1
%by Kaplan-Meier estimate with the log-rank test P-value as 0.0495. The \acrshort{egfr} is identified as one of those poor prognostic factors as well. %However, it is far from the top 20 candidates.
%(please see https://github.com/texchi2/\linebreak
%pvalueTex/blob/master/HNSCC\_OS\_marginS\_6429.csv for reference, the table was ranked by FDR P-value)

% transforming growth factor- (TGF-α) 
% epidermal growth factor receptor (EGFR)
%As in our manuscript mentioned, In a multivariate analysis, tumor site, tumor level of \acrshort{egfr}, and tumor level of TGF-$\alpha$ (\acrshort{egfr} ligand) were statistically significant predictors of disease-free survival of \acrshort{hnscc} patients\cite{Rusch1996}\cite{Grandis1998}.
%Since that breakthrough discovery and validation, the \acrshort{egfr} monoclonal antibody (cetuximab)\cite{Bonner2006a} and \acrshort{egfr} \acrshort{tki} (such as gefitinib, erlotinib, osimertinib) were developed to treat advanced \acrshort{hnscc}. Although 90\% of \acrshort{hnscc} has overexpression of \acrshort{egfr}, cetuximab has only 10\% to 20\% response rate on those patients\cite{Johnson2020}. So far, cetuximab is still the only drug of choice with proven efficacy, which targeted the selected \acrshort{hnscc} patients\cite{Taberna2019}.
%citing the line number and exact change, marked in \textcolor{red}{Red from page 6 (line 16) to page 7 (line 17)}
%Thus, we wish the further validations of our meaningful hypotheses of the candidate to explore more useful drug of choice in the treatment of \acrshort{hnscc} patients.
% a list from literature review, 留 下少於  50 articles mentioned candidates
%HNSCC_survivalAnalysis_marginS_EGFR.Rda
%HNSCC_survivalAnalysis_marginS_EGFR.xlsx
%https://github.com/texchi2/pvalueTex/blob/master/file20500_list.txt
%analysis_export.R to generate https://github.com/texchi2/pvalueTex/blob/master/HNSCC_OS_marginS_6429.csv
\end{MyColorPar}

\subsection*{1-2}
Half of the discussion part was occupied with holistic and spiritual influence on patient’s survival.
The latter half of the discussion may not be appropriate for this manuscript. Many people aware of the relationship between prognosis and mental/financial/familial situations. Unfortunately, almost all authors do not understand why half of the discussion part was occupied with spiritual something. Isn’t it a totally different theme from biomarkers of HNSCC?
Stress may affect the expression level of these biomarkers, which may result in an unexpected prognosis, the main theme of this manuscript is different. If you want to describe spiritual something, please submit it as a brand new manuscript.
Please remember my opinion does not intend to insult your religion because I am also a Buddhist and morning meditation always allow me to start a wonderful day.

%DNA alteration (mutation/amplification) is also an influential prognostic factor, but I would like to know if DNA alteration is considered in this analysis.
%[如果加入 DNA alteration 又會如何? 不佳; 選擇 mRNA 的原因是? interpretability and drugable: EGFR]

@@

One day in February 2021, after meditation in the morning, the first author (Dr. Chi) has raised this idea then wrote it in discussion section with comprehensive references. Dr. Chi want to say "Stress is also be a kind of biomarker of HNSCC in the future study".
We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care. We will brief this issue and move rest of it in the other manuscript.

The summary of holistic cancer care in this revised manuscript could be:
"
".

%Those different types of omics data measured for the same patients (called multi-omics data) are currently under investigation across several disciplines such as genomics (i.e., DNA mutation/amplification, single nucleotide polymorphisms), %copy number variation), 
%epigenomics, transcriptomics (i.e., RNA expression), proteomics, metabolomics, and microbiomics.
%The usefulness of multi-omics data for the prediction of HNSCC outcome %is expected.
%such as the (censored) survival time.

\end{MyColorPar}
\pagebreak
%======
\section*{Response to Reviewer 2 Comments}
%Response to Referees} % rebuttal
We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript. The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}). 
Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.

Comments and Suggestions for Authors from the reviewer \#2 % 善意提醒、指導

The authors introduced a workflow to identify gene-expression biomarkers based on TCGA data and applied it to head and neck squamous cell carcinoma. The authors tried to highlight their workflow and present it as a new tool, however, their workflow is very common, and I cannot see its novelty. 
The selection of gene expression cutoff is not well handled statistically (see below my first comment). 
Therefore, I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them. % new Title, abstract, change tone
Exploring all possible expression cutoffs is also usable but should only be used for established biomarkers. Once it is known that a gene is a strong biomarker (e.g., from a genome-wide test using fixed cutoffs), one can fine-tune the cutoffs utilizing this strategy.

\subsection*{2-1}
Exploring all possible expression cutoffs is controversial. A robust expression biomarker should be effective and detectable at most major cutoffs. Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05). For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff. But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. This strategy only identifies more weak “biomarkers,” and it also captures more false positives. 
Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.

@@

We appreciate the reviewer for the question allowing discussing TCGA in detail.\\

[after cut-off finding]
Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.

***=> Bonferroni correction should be used in final decision.
%位置要換一下：
The false discovery rate
645 (FDR) (< 0.05) could be used to pick up the optimal P value to ensure the control for
646 type I error of the Kaplan-Meier survival test during the cutoff finding procedure.
4.2. Cutoff Finder Core Engine.

..
%To the best of our knowledge, TCGA "HNSC"(they coded) is the only single and largest collection of whole-genome sequencing and clinical survival dataset in the field of HNSCC research so far.

%After that, there are 18,082 cross-cancer type articles produced using the TCGA database. The 778 publications (Figure \ref{figure:fig_embase}, b. 778) among them were focused on HNSCC research. Those occupied about 18\% of HNSCC research articles with genetic-related topics during the same time. Thus, about 60 TCGA HNSCC articles were published worldwide per year since 2008. %\ref{figure:fig_embase}
\begin{figure}
\raggedleft
\includegraphics[width=14cm]{Answer_2-1.pdf}
\caption{Cancer research articles published from 2008 to 2021. Total: 2.4 million; genetic related: 0.6 million; HNSCC research: 12,636.}
\label{figure:fig_embase}
\end{figure}
\clearpage
%778/4350 = 17.9\% using TCGA data
%There is 374 genes in the oral cancer gene database of Indian HNSCC; http://www.bioinformation.net/006/97320630006169.pdf
%http://www.actrec.gov.in/OCDB/index.htm

@@

\subsection*{2-2}
I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them. % new Title, abstract, change tone

@@

We appreciate the reviewer for the critical comment.
We change new Title, abstract, change tone

@@

\subsection*{2-3}
% strategy should changing
In the independent test, half genes have p-values less than 0.05, and most of them have p-values >0.01. Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. The p-values are affected by the sample size, which should be described in the main text. As I mentioned above, the authors should look for more data to verify these biomarkers.

@@

We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
% ???
% x
%how to apply or modify the R scripts to use on other datasets
%\begin{itemize} %summarize the elements of the workflow
\begin{outline}
The data from TCGA database or other databases could be applied by this workflow, since modification of the R script is necessary to adapt the difference structure among datasets (e.x. data schema, table size, definition of features, number of features and their location on the table column).\\
In short, the elements of the workflow with the \{codes\} shows:\\
(please also see Figure \ref{fig:workflow})
\1 $[\# step 1 (main)]$
\{main\_marginSFP\_HNSCC.R\}
        \2 dataset retrieval from TCGA GDC data portal (in GDAC format)
%\1 $[\# step 1]$
    \2 \{TCGA\_HNSCC\_marginSFP.R\}
        \3 \underline{raw data cleaning}
        \3 \underline{data transformation and merge}
        \3 \underline{dichotomization of clinical features}
%     \item Using a serial cut from 30\% to 70\% percentile of the cohort, it could find the least P-value cutoff of the Kaplan-Meier analysis for each gene expression.
        \3 survival analysis
            \4 cut off finder by \{cutofFinder\_func\_HNSCC.R\}
%     \item The R script program could automatically scan protein-coding genes and generate the Kaplan-Meier plots and Cox's univariate/multivariate tables.
            \4 Cox modelling
\1 $[\# step 2]$
\{analysis\_export.R\}
    \2 analysis of the tables generated from \# step 1
    \2 candidate selection
%    \item Our analysis could discover the pronounced biomarkers, which impact HNSCC's survival under the stringent Bonferroni adjustment.
\1 (remark: only the \underline{underlined} portion in \{TCGA\_HNSCC\_marginSFP.R\} should be re-coded aggressively)
\end{outline}

@@

% #####################
\subsection*{2-4}
How univariable and multivariable tests work should be clearly described in the main text. In a multivariable test, which variables were used?
Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.

@@

\begin{MyColorPar}{red}

"The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005."

\end{MyColorPar}   % marked in red above
